### 2017-04-05 paper/modes.tex
final pass on modes.tex

Notice that an important aspect in deciding which configuration to use
(or in designing new test suites) is the possibility of race
conditions on shared data during execution.  Data sharing can occur
through state that is reachable from statically-declared variables in
the program or through variables declared within the scope of the test
class~\cite{luo-etal-fse2014}.  Considering data race avoidance,
intuitively, configuration \SeqClassParMeth{} is preferable over
\ParClassSeqMeth{} when it is clear that test methods in a class do
not manipulate shared state, which can be challenging to
determine~\cite{bell-etal-esecfse2015}, whereas \ParClassSeqMeth{} is
preferable over \SeqClassParMeth{} when it is clear that several test
methods in one class perform operations involving shared data.
Configuration \ParClassParMeth{} is more likely to manifest data races
during execution as it does not restrict scheduling orderings. Note
that speedups depend on several factors, including the test suite size
and distribution of test methods per class.

@@

Forking OS processes to run test jobs is a popular mechanism of build
systems to obtain parallelism at the machine space (see
Figure~\ref{fig:levels}).  For Java-based systems (e.g., Maven and
Ant), this amounts to spawning one JVM instance (per process) per CPU,
on a machine with potentially many virtual CPUs, and aggregating
corresponding results when jobs finish.  Note that forking can only be
combined with configuration \SeqClassParMeth{} (see
Section~\ref{sec:frameworks}) as Maven only accepts one test class at
a time per forked process.  To attenuate the non-trivial cost of
spawning new processes and JVMs on every test class, Maven offers an
option to reuse the JVM.

@@

\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
fragment of a Maven configuration file, known as \pomf{}, highlighting
options to run tests using the parallel execution mode \ForkParMeth{}.
With this configuration, Maven~---~through its test plugin
Surefire~\cite{maven-surefire-plugin}~---~forks one JVM per core
(\CodeIn{forkCount} parameter) and uses five threads
(\CodeIn{threadCount} parameter) to run methods (\CodeIn{parallel}
parameter) within each forked JVM. After the execution of a test
class, Maven reuses the forked JVM for the next execution
(\CodeIn{reuseFork} parameter).

%%  LocalWords:  parallelization CPUs JUnit TestNG NUnit multi JVM de
%%  LocalWords:  JVMs falar explicar configuracao ilustrada levanta
%%  LocalWords:  uma por cria cada executar paralelo escapeinside
%%  LocalWords:  xleftmargin framexleftmargin basicstyle boxpos
%%  LocalWords:  numberstyle morekeywords threadCount forkCount
%%  LocalWords:  perCoreThreadCount reuseFork deletekeywords groupId
%%  LocalWords:  artifactId

>>>>

Notice that an important aspect in deciding which configuration to use
(or in designing new test suites) is the possibility of race
conditions on shared data during execution.  Data sharing can occur
through state that is reachable from statically-declared variables in
the program or through variables declared within the scope of the test
class~\cite{luo-etal-fse2014}.  Considering data race avoidance,
configuration \SeqClassParMeth{} is preferable over \ParClassSeqMeth{}
when it is clear that test methods in a class do not manipulate shared
state, which can be challenging to
determine~\cite{bell-etal-esecfse2015}.  Similarly, \ParClassSeqMeth{}
is preferable over \SeqClassParMeth{} when it is clear that several
test methods in a class perform operations involving shared data.
Configuration \ParClassParMeth{} does not restrict scheduling
orderings.  Consequently, it is more likely to manifest data races
during execution. Note that speedups depend on several factors,
including the test suite size and distribution of test methods per
class.

@@

Forking OS processes to run test jobs is a popular mechanism of build
systems to obtain parallelism at the machine space (see
Figure~\ref{fig:levels}).  For Java-based build systems, such as Maven
and Ant, this amounts to spawning one JVM instance to handle a test
job and aggregating corresponding results when test jobs finish.  Note
that forking can only be combined with configuration
\SeqClassParMeth{} (see Section~\ref{sec:frameworks}) as Maven only
accepts one test class at a time per forked process.  To attenuate the
non-trivial cost of spawning new JVM processes on every test class,
Maven offers an option to reuse the JVM.

@@

\subsubsection*{Example}~Figure~\ref{fig:surefire} shows a
fragment of a Maven configuration file, known as \pomf{}, highlighting
options to run tests using the parallel execution mode \ForkParMeth{}.
Maven implements this feature through its JUnit test plugin
Surefire~\cite{maven-surefire-plugin}.  With this configuration, Maven
forks one JVM per core (\CodeIn{forkCount} parameter) and uses five
threads (\CodeIn{threadCount} parameter) to run test methods
(\CodeIn{parallel} parameter) within each forked JVM.  Maven reuses
created JVMs on subsequent forks when execution of a test class
terminates (\CodeIn{reuseFork} parameter).

%%  LocalWords:  parallelization CPUs JUnit TestNG NUnit multi JVM de
%%  LocalWords:  JVMs falar explicar configuracao ilustrada levanta
%%  LocalWords:  uma por cria cada executar paralelo escapeinside
%%  LocalWords:  xleftmargin framexleftmargin basicstyle boxpos
%%  LocalWords:  numberstyle morekeywords threadCount forkCount
%%  LocalWords:  perCoreThreadCount reuseFork deletekeywords groupId
%%  LocalWords:  artifactId reuseForks
